FTLR proof cases

### 2018-04-13 fully-abstract-comp/ftlr-proof-cases.tex
Prove simple lemma.

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}

>>>>

\begin{lemma}[purePart is idempotent]
  For all $W$, $\purePart(\purePart(W)) = \purePart(W)$
  \label{lem:purePart-idempotent}
\end{lemma}
\begin{proof}
  Follows easily from the definition.
\end{proof}

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}
\begin{proof}
  Follows easily by inspecting the definitions of $\lrv$, $\readCond$, $\addressable$, $\writeCond$, $\execCond$ and $\xReadCond$ and using Lemma~\ref{lem:purePart-idempotent}.
\end{proof}
